data_cleaning

### 2015-11-29 analysis/exp_data_clean.Rmd
created e10 data set with laplace smoothing (added one to each literal listener condition)

>>>>

### Smoothing for e10
```{r}
NUM_ITEMS = 5
ms.smoothing = d %>%
  mutate(stars = as.numeric(as.character(stars))/20) %>%
  group_by(scale, degree, stars) %>%
  summarise(cil = ci.low(judgment), 
            cih = ci.high(judgment), 
            cnt.judgment = sum(judgment) + 1,
            speaker.p2 = cnt.judgment / (n() + 1),
            speaker.p = mean(judgment))
ms.smoothing

write.csv(ms, "../models/model_data/L0_e10_laplace.csv", row.names=FALSE)
```
